### 2020-05-16 learning Logic/draft.tex
a

\vspace{20pt}
\textbf{Points from the discussion on 13.05.2020:}
	\begin{itemize}
		\item We assume that the robot has the labelling of the whole system beforehand for now. We can consider the other case later.
		\item Use RRG instead of RRT so that we can go back also. But in RRG, multiple transitions can be added with each sampled state. \kush{Will have to change the implementation a bit.}
		\item \textbf{What we need from the SAMPLE procedure:} Given a pair of set of states (fromStates, toStates) in the abstract system (formulas over the APs of the system), SAMPLE should return a newly sampled transition from a state where 'fromState' is \textit{true} to a state where 'toState' is \textit{true}. It maybe the case that such a transition doesn't exist or probability of it being sampled is very small, in that case, return \emph{null} after some given threshold time/samples.\newline
		\textbf{How do we do this with RRG?}
		\begin{itemize}
			\item Each node in the graph ($G$) will store the APs associated with it. 
			\item If the whole tree is stored as a BDD, finding nodes where 'fromStates' is very easy but storing it in a BDD is very difficult. \kush{Find a way to do both the things efficiently.}
			\item 
		\end{itemize}

		\item \textbf{Jan's idea:} We can keep track of the sampled transitions till now and get their ranking (finding ranking for each sampled transition will require some time because it might have to pass through the whole list of 'reachableStates'). Sample 50 (some threshold) transitions and add the one with the best rank. \kush{What will happen to the other transitions? Would we keep all of them in the memory (maintain a min-heap maybe)?}
	\end{itemize}

>>>>

\vspace{20pt}
\textbf{Points from the discussion on 13.05.2020:}
	\begin{itemize}
		\item We assume that the robot has the labelling of the whole system beforehand for now. We can consider the other case later.

		\item Use RRG instead of RRT so that we can go back also.

		\item \textbf{What we need from the SAMPLE procedure:} Given a pair of set of states (fromStates, toStates) in the abstract system (formulas over the APs of the system), SAMPLE should return a newly sampled transition from a state where `fromState' is \textit{true} to a state where `toState' is \textit{true}. It maybe the case that such a transition doesn't exist or probability of it being sampled is very small, in that case, return \emph{null} after some given threshold time/samples.\newline
		\textbf{How do we do this with RRG?}
		\begin{itemize}
			\item Each node in the graph ($G$) will store the APs associated with it. 
			\item If the whole tree is stored as a BDD, finding nodes where `fromStates' is very easy but storing it in a BDD is very difficult. \kush{Find a way to do both the things efficiently.}
		\end{itemize}

		\item \textbf{Jan's idea:} We can keep track of the sampled transitions till now and get their ranking (finding ranking for each sampled transition will require some time because it might have to pass through the whole list of `reachableStates'). Sample 50 (some threshold) transitions and add the one with the best rank. \kush{What will happen to the other transitions? Would we keep all of them in the memory (maintain a min-heap maybe)?}
	\end{itemize}
